---
title: "PowerBI"
author: "Danny Rasch"
date: '2017-03-09'
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
  pdf_document:
    number_sections: yes
geometry: margin = 1.2in
fontsize: 10pt
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

#Load Dataset
```{r}
file="Boxplot1.csv"
file="NFF_1.csv"

dataset=read.csv(file,sep=",")

colnames(dataset)
str(dataset)
types=sapply(dataset, class)
types[2][1]=="factor"


Type1=types[2]



#### Option 2
testVect <-sapply(dataset, class)

######Example
testVect <- structure(c("11.2.0.3.0", "12.89", "12.71"), .Names = c("db_version", 
             "elapsed_time", "cpu_time"))

#Named Characters to dataFrame
data.frame(as.list(testVect))
#Or if you want sensible data types for your columns
datatypes<-data.frame(lapply(testVect, type.convert), stringsAsFactors=FALSE)
#############3


datatypes[1,1]=="factor"
datatypes[1,2]=="factor"

```

# Libraries

```{r}
library(ggplot2)
library(plotly)
```

## Boxplot1

```{r pressure, echo=FALSE}
#str(dataset)
#sapply(dataset, class)


d <-dataset

p<-ggplot(data=d,mapping=aes(x=d$Symbol,y=d[,2]))
p<-p+geom_boxplot()
p

P <- ggplotly(p)
P

```


# 24 BOXPLOT WITH VARIABLE WIDTH


Input

X=Factor
Y=Numeric
Color=Factor (Default color scheme)



## Example


```{r}
#Creating data 
names=c(rep("A", 20) , rep("B", 8) , rep("C", 30), rep("D", 80))
value=c( sample(2:5, 20 , replace=T) , sample(4:10, 8 , replace=T), 
       sample(1:7, 30 , replace=T), sample(3:8, 80 , replace=T) )
data=data.frame(names,value)
 
 
# Calculate proportion of each level
proportion=table(data$names)/nrow(data)
 
#Draw the boxplot, with the width proportionnal to the occurence !
boxplot(data$value ~ data$names , width=proportion , col=c("orange" , "seagreen"))
 

```

## Adapted

```{r}
# Calculate proportion of each level
proportion=table(dataset[,1])/nrow(dataset)
 
#Set color
##################################### To do


#Draw the boxplot, with the width proportionnal to the occurence !
p=boxplot(dataset[,2] ~ dataset[,1] , width=proportion , col=c("orange" , "seagreen"))
p
```


# Boxplot2

Input

X=Factor
Y=Numeric
Fill=Factor

## Example

```{r}
library(ggthemes)
g <- ggplot(mpg, aes(class, cty))
g + geom_boxplot(aes(fill=factor(cyl))) + 
  theme(axis.text.x = element_text(angle=65, vjust=0.6)) + 
  labs(title="Box plot", 
       subtitle="City Mileage grouped by Class of vehicle",
       caption="Source: mpg",
       x="Class of Vehicle",
       y="City Mileage")
```


## Original

```{r}

```


## Customized

# Boxplot & Dots

On top of the information provided by a box plot, the dot plot can provide more clear information in the form of summary statistics by each group. The dots are staggered such that each dot represents one observation. So, in below chart, the number of dots for a given manufacturer will match the number of rows of that manufacturer in source data.

```{r}
library(ggplot2)
theme_set(theme_bw())

# plot
g <- ggplot(mpg, aes(manufacturer, cty))
g + geom_boxplot() + 
  geom_dotplot(binaxis='y', 
               stackdir='center', 
               dotsize = .5, 
               fill="red") +
  theme(axis.text.x = element_text(angle=65, vjust=0.6)) + 
  labs(title="Box plot + Dot plot", 
       subtitle="City Mileage vs Class: Each dot represents 1 row in source data",
       caption="Source: mpg",
       x="Class of Vehicle",
       y="City Mileage")
```


# Boxplot with Plot_ly

## Basic

### Example
```{r}
library(plotly)
p <- plot_ly(y = ~rnorm(50), type = "box") #%>%
  #add_trace(y = ~rnorm(50, 1))
p
```
### Dataset

```{r}
### PREP
Y=dataset[,2]
###

library(plotly)
p <- plot_ly(y = Y, type = "box") 
p
```


## Horizontal Boxplot

```{r}
library(plotly)
p <- plot_ly(x = ~rnorm(50), type = "box") %>%
  add_trace(x = ~rnorm(50, 1))
p
```

### Dataset

```{r}
### PREP
X=dataset[,2]
###

library(plotly)
p <- plot_ly(x = X, type = "box") 
p
```

## Adding Jittered Points

### Example
```{r}
p <- plot_ly(y = ~rnorm(50), type = "box", boxpoints = "all", jitter = 0.3,
        pointpos = -1.8)
p
```
### Dataset

```{r}
### PREP
Y=dataset[,2]
###

p <- plot_ly(y = Y, type = "box", boxpoints = "all", jitter = 0.3,
        pointpos = -1.8)
p
```

## Several Box Plots

### Example
```{r}
p <- plot_ly(ggplot2::diamonds, y = ~price, color = ~cut, type = "box")
p
```

### Dataset
```{r}
### PREP
Y=dataset[,2]
COLOR=dataset[,1]
###

p <- plot_ly(dataset, y = Y, color = COLOR, type = "box")
p
```


## Grouped Box Plots

### Example

```{r}
p <- plot_ly(ggplot2::diamonds, x = ~cut, y = ~price, color = ~clarity, type = "box") %>%
  layout(boxmode = "group")
p

```


### Dataset Verson: A
```{r}
### PREP
X=dataset[,1]
Y=dataset[,2]
COLOR=dataset[,3]
###

p <- plot_ly(dataset, x = X, y = Y, color = COLOR, type = "box") %>%
  layout(boxmode = "group")
p
```
### Dataset Verson: B
```{r}
### PREP
X=dataset[,3]
Y=dataset[,2]
COLOR=dataset[,1]
###

p <- plot_ly(dataset, x = X, y = Y, color = COLOR, type = "box") %>%
  layout(boxmode = "group")
p
```
## Styling Outliers

```{r}
library(plotly)

y1 <- c(0.75, 5.25, 5.5, 6, 6.2, 6.6, 6.80, 7.0, 7.2, 7.5, 7.5, 7.75, 8.15,
       8.15, 8.65, 8.93, 9.2, 9.5, 10, 10.25, 11.5, 12, 16, 20.90, 22.3, 23.25)
y2 <- c(0.75, 5.25, 5.5, 6, 6.2, 6.6, 6.80, 7.0, 7.2, 7.5, 7.5, 7.75, 8.15,
        8.15, 8.65, 8.93, 9.2, 9.5, 10, 10.25, 11.5, 12, 16, 20.90, 22.3, 23.25)
y3 <- c(0.75, 5.25, 5.5, 6, 6.2, 6.6, 6.80, 7.0, 7.2, 7.5, 7.5, 7.75, 8.15,
        8.15, 8.65, 8.93, 9.2, 9.5, 10, 10.25, 11.5, 12, 16, 20.90, 22.3, 23.25)
y4 <- c(0.75, 5.25, 5.5, 6, 6.2, 6.6, 6.80, 7.0, 7.2, 7.5, 7.5, 7.75, 8.15,
        8.15, 8.65, 8.93, 9.2, 9.5, 10, 10.25, 11.5, 12, 16, 20.90, 22.3, 23.25)

p <- plot_ly(type = 'box') %>%
  add_boxplot(y = y1, jitter = 0.3, pointpos = -1.8, boxpoints = 'all',
              marker = list(color = 'rgb(7,40,89)'),
              line = list(color = 'rgb(7,40,89)'),
              name = "All Points") %>%
  add_boxplot(y = y2, name = "Only Whiskers", boxpoints = FALSE,
              marker = list(color = 'rgb(9,56,125)'),
              line = list(color = 'rgb(9,56,125)')) %>%
  add_boxplot(y = y3, name = "Suspected Outlier", boxpoints = 'suspectedoutliers',
              marker = list(color = 'rgb(8,81,156)',
                            outliercolor = 'rgba(219, 64, 82, 0.6)',
                            line = list(outliercolor = 'rgba(219, 64, 82, 1.0)',
                                        outlierwidth = 2)),
              line = list(color = 'rgb(8,81,156)')) %>%
  add_boxplot(y = y4, name = "Whiskers and Outliers", boxpoints = 'outliers',
              marker = list(color = 'rgb(107,174,214)'),
              line = list(color = 'rgb(107,174,214)')) %>%
  layout(title = "Box Plot Styling Outliers")
p
```


# Violin Plot

```{r}
library(ggplot2)
theme_set(theme_bw())

# plot
g <- ggplot(mpg, aes(class, cty))
g + geom_violin() + 
  labs(title="Violin plot", 
       subtitle="City Mileage vs Class of vehicle",
       caption="Source: mpg",
       x="Class of Vehicle",
       y="City Mileage")

######## Not working
#library(plotly)
#P <- ggplotly(g)
#P
```







# 94 VIOLIN PLOT

http://www.r-graph-gallery.com/94-violin-plot/

```{r}
# Charge the vioplot library
library(vioplot)
 
# Create data
treatment=c(rep("A", 40) , rep("B", 40) , rep("C", 40) )
value=c( sample(2:5, 40 , replace=T) , sample(c(1:5,12:17), 40 , replace=T), sample(1:7, 40 , replace=T) )
data=data.frame(treatment,value)
 
# Draw the plot
with(data , vioplot( value[treatment=="A"] , value[treatment=="B"], value[treatment=="C"],  col=rgb(0.1,0.4,0.7,0.7) , names=c("A","B","C") ))
 

```

## Adaption ???

```{r}
# Draw the plot
with(data , vioplot( value[treatment=="A"] , value[treatment=="B"], value[treatment=="C"],  col=rgb(0.1,0.4,0.7,0.7) , names=c("A","B","C") ))
 

```










# http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html


# Scatterplot

```{r}
# install.packages("ggplot2")
# load package and data
options(scipen=999)  # turn-off scientific notation like 1e+48
library(ggplot2)
theme_set(theme_bw())  # pre-set the bw theme.
data("midwest", package = "ggplot2")
# midwest <- read.csv("http://goo.gl/G1K41K")  # bkup data source

# Scatterplot
gg <- ggplot(midwest, aes(x=area, y=poptotal)) + 
  geom_point(aes(col=state, size=popdensity)) + 
  geom_smooth(method="loess", se=F) + 
  xlim(c(0, 0.1)) + 
  ylim(c(0, 500000)) + 
  labs(subtitle="Area Vs Population", 
       y="Population", 
       x="Area", 
       title="Scatterplot", 
       caption = "Source: midwest")

plot(gg)
```

4 


x=NUMERIC
y=integer

col=factor
size=numeric

```{r}
X=dataset[,2]
Y=dataset[,2]

COL=dataset[,1]
SIZE=dataset[,2]


```





```{r}
# Scatterplot
gg <- ggplot(dataset, aes(x=X, y=Y)) + 
  geom_point(aes(col=COL, size=SIZE)) + 
  geom_smooth(method="loess", se=F) + 
  xlim(c(0, 50)) + 
  ylim(c(0, 50)) + 
  labs(subtitle="Area Vs Population", 
       y="Population", 
       x="Area", 
       title="Scatterplot", 
       caption = "Source: midwest")

plot(gg)
```

# Density Plot

For

numeric
numeric
factor


```{r}
library(ggplot2)
theme_set(theme_classic())

# Plot
g <- ggplot(mpg, aes(cty))
g + geom_density(aes(fill=factor(cyl)), alpha=0.8) + 
    labs(title="Density plot", 
         subtitle="City Mileage Grouped by Number of cylinders",
         caption="Source: mpg",
         x="City Mileage",
         fill="# Cylinders")
```


# Composition

## Waffle

```{r}
var <- mpg$class  # the categorical data 

## Prep data (nothing to change here)
nrows <- 10
df <- expand.grid(y = 1:nrows, x = 1:nrows)
categ_table <- round(table(var) * ((nrows*nrows)/(length(var))))
categ_table
#>   2seater    compact    midsize    minivan     pickup subcompact        suv 
#>         2         20         18          5         14         15         26 

df$category <- factor(rep(names(categ_table), categ_table))  
# NOTE: if sum(categ_table) is not 100 (i.e. nrows^2), it will need adjustment to make the sum to 100.

## Plot
ggplot(df, aes(x = x, y = y, fill = category)) + 
        geom_tile(color = "black", size = 0.5) +
        scale_x_continuous(expand = c(0, 0)) +
        scale_y_continuous(expand = c(0, 0), trans = 'reverse') +
        scale_fill_brewer(palette = "Set3") +
        labs(title="Waffle Chart", subtitle="'Class' of vehicles",
             caption="Source: mpg") + 
        theme(panel.border = element_rect(size = 2),
              plot.title = element_text(size = rel(1.2)),
              axis.text = element_blank(),
              axis.title = element_blank(),
              axis.ticks = element_blank(),
              legend.title = element_blank(),
              legend.position = "right")
```


## Pie Chart

http://www.r-graph-gallery.com/128-ring-or-donut-plot/

```{r}
library(ggplot2)
theme_set(theme_classic())

# Source: Frequency table
df <- as.data.frame(table(mpg$class))
colnames(df) <- c("class", "freq")
pie <- ggplot(df, aes(x = "", y=freq, fill = factor(class))) + 
  geom_bar(width = 1, stat = "identity") +
  theme(axis.line = element_blank(), 
        plot.title = element_text(hjust=0.5)) + 
  labs(fill="class", 
       x=NULL, 
       y=NULL, 
       title="Pie Chart of class", 
       caption="Source: mpg")

pie + coord_polar(theta = "y", start=0)

# Source: Categorical variable.
# mpg$class
pie <- ggplot(mpg, aes(x = "", fill = factor(class))) + 
  geom_bar(width = 1) +
  theme(axis.line = element_blank(), 
        plot.title = element_text(hjust=0.5)) + 
  labs(fill="class", 
       x=NULL, 
       y=NULL, 
       title="Pie Chart of class", 
       caption="Source: mpg")
  
pie + coord_polar(theta = "y", start=0)
```



## Treemap

http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html

```{r}

library(ggplot2) 
library(treemapify)
proglangs <- read.csv("https://raw.githubusercontent.com/selva86/datasets/master/proglanguages.csv")

# plot
treeMapCoordinates <- treemapify(proglangs,
                                 area = "value",
                                 fill = "parent",
                                 label = "id",
                                 group = "parent")


#Not working
#treeMapPlot <- ggplotify(treeMapCoordinates) + 
#                  scale_x_continuous(expand = c(0, 0)) +
#                  scale_y_continuous(expand = c(0, 0)) +
#                  scale_fill_brewer(palette = "Dark2")

#print(treeMapPlot)

```



# Calendar Heatmap

```{r}
# http://margintale.blogspot.in/2012/04/ggplot2-time-series-heatmaps.html
library(ggplot2)
library(plyr)
library(scales)
library(zoo)

df <- read.csv("https://raw.githubusercontent.com/selva86/datasets/master/yahoo.csv")
df$date <- as.Date(df$date)  # format date
df <- df[df$year >= 2012, ]  # filter reqd years

# Create Month Week
df$yearmonth <- as.yearmon(df$date)
df$yearmonthf <- factor(df$yearmonth)
df <- ddply(df,.(yearmonthf), transform, monthweek=1+week-min(week))  # compute week number of month
df <- df[, c("year", "yearmonthf", "monthf", "week", "monthweek", "weekdayf", "VIX.Close")]
head(df)
#>   year yearmonthf monthf week monthweek weekdayf VIX.Close
#> 1 2012   Jan 2012    Jan    1         1      Tue     22.97
#> 2 2012   Jan 2012    Jan    1         1      Wed     22.22
#> 3 2012   Jan 2012    Jan    1         1      Thu     21.48
#> 4 2012   Jan 2012    Jan    1         1      Fri     20.63
#> 5 2012   Jan 2012    Jan    2         2      Mon     21.07
#> 6 2012   Jan 2012    Jan    2         2      Tue     20.69


# Plot
ggplot(df, aes(monthweek, weekdayf, fill = VIX.Close)) + 
  geom_tile(colour = "white") + 
  facet_grid(year~monthf) + 
  scale_fill_gradient(low="red", high="green") +
  labs(x="Week of Month",
       y="",
       title = "Time-Series Calendar Heatmap", 
       subtitle="Yahoo Closing Price", 
       fill="Close")
```


```{r}
# devtools::install_github("hrbrmstr/ggalt")
library(ggplot2)
library(ggalt)
library(ggfortify)
theme_set(theme_classic())

# Compute data with principal components ------------------
df <- iris[c(1, 2, 3, 4)]
pca_mod <- prcomp(df)  # compute principal components

# Data frame of principal components ----------------------
df_pc <- data.frame(pca_mod$x, Species=iris$Species)  # dataframe of principal components
df_pc_vir <- df_pc[df_pc$Species == "virginica", ]  # df for 'virginica'
df_pc_set <- df_pc[df_pc$Species == "setosa", ]  # df for 'setosa'
df_pc_ver <- df_pc[df_pc$Species == "versicolor", ]  # df for 'versicolor'
 
# Plot ----------------------------------------------------
ggplot(df_pc, aes(PC1, PC2, col=Species)) + 
  geom_point(aes(shape=Species), size=2) +   # draw points
  labs(title="Iris Clustering", 
       subtitle="With principal components PC1 and PC2 as X and Y axis",
       caption="Source: Iris") + 
  coord_cartesian(xlim = 1.2 * c(min(df_pc$PC1), max(df_pc$PC1)), 
                  ylim = 1.2 * c(min(df_pc$PC2), max(df_pc$PC2))) +   # change axis limits
  geom_encircle(data = df_pc_vir, aes(x=PC1, y=PC2)) +   # draw circles
  geom_encircle(data = df_pc_set, aes(x=PC1, y=PC2)) + 
  geom_encircle(data = df_pc_ver, aes(x=PC1, y=PC2))
```

8. Spatial
The ggmap package provides facilities to interact with the google maps api and get the coordinates (latitude and longitude) of places you want to plot. The below example shows satellite, road and hybrid maps of the city of Chennai, encircling some of the places. I used the geocode() function to get the coordinates of these places and qmap() to get the maps. The type of map to fetch is determined by the value you set to the maptype.

You can also zoom into the map by setting the zoom argument. The default is 10 (suitable for large cities). Reduce this number (up to 3) if you want to zoom out. It can be zoomed in till 21, suitable for buildings.
```{r, eval=FALSE, include=FALSE}
# Better install the dev versions ----------
# devtools::install_github("dkahle/ggmap")
# devtools::install_github("hrbrmstr/ggalt")

# load packages
library(ggplot2)
library(ggmap)
library(ggalt)

# Get Chennai's Coordinates --------------------------------
chennai <-  geocode("Chennai")  # get longitude and latitude

# Get the Map ----------------------------------------------
# Google Satellite Map
chennai_ggl_sat_map <- qmap("chennai", zoom=12, source = "google", maptype="satellite")  

# Google Road Map
chennai_ggl_road_map <- qmap("chennai", zoom=12, source = "google", maptype="roadmap")  

# Google Hybrid Map
chennai_ggl_hybrid_map <- qmap("chennai", zoom=12, source = "google", maptype="hybrid")  

# Open Street Map
chennai_osm_map <- qmap("chennai", zoom=12, source = "osm")   

# Get Coordinates for Chennai's Places ---------------------
chennai_places <- c("Kolathur",
                    "Washermanpet",
                    "Royapettah",
                    "Adyar",
                    "Guindy")

places_loc <- geocode(chennai_places)  # get longitudes and latitudes


# Plot Open Street Map -------------------------------------
chennai_osm_map + geom_point(aes(x=lon, y=lat),
                             data = places_loc, 
                             alpha = 0.7, 
                             size = 7, 
                             color = "tomato") + 
                  geom_encircle(aes(x=lon, y=lat),
                                data = places_loc, size = 2, color = "blue")

# Plot Google Road Map -------------------------------------
chennai_ggl_road_map + geom_point(aes(x=lon, y=lat),
                                  data = places_loc, 
                                  alpha = 0.7, 
                                  size = 7, 
                                  color = "tomato") + 
                       geom_encircle(aes(x=lon, y=lat),
                                     data = places_loc, size = 2, color = "blue")

# Google Hybrid Map ----------------------------------------
chennai_ggl_hybrid_map + geom_point(aes(x=lon, y=lat),
                                     data = places_loc, 
                                     alpha = 0.7, 
                                     size = 7, 
                                     color = "tomato") + 
                          geom_encircle(aes(x=lon, y=lat),
                                        data = places_loc, size = 2, color = "blue")
```

