---
title: "FRTB Prototype for IRSWaps"
author: "Danny Rasch"
date: '2017-03-09'
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
  pdf_document:
    number_sections: yes
geometry: margin = 1.2in
fontsize: 10pt
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r}
#setwd("c:/FRTB/_Portfolio_01") 
#load("myfile.RData")
```

## Including Plots

# fdsfsd
```{r LoadInput, message=FALSE, warning=FALSE}
library(tidyquant)
library(ggplot2)
data(FANG)
FANG
## test ###########
#### Overwrite FANG
currentPath=getwd()
setwd("C:/OneDrive/PowerBI_test/Portfolio_Slicer/Input")

library(data.table)
Quotes <- fread("C:/OneDrive/PowerBI_test/Portfolio_Slicer/Input/Quotes_detail.csv")
Quotes$date = as.Date(Quotes$date)


#Quotes=as.data.frame(Quotes)
Quotes <- subset(Quotes, symbol == "SIE.DE" | symbol == "CBK.DE" | symbol == "2PP.F"| symbol == "BAYN.DE"| symbol == "FTK.DE")



########               does strange things
##Quotes = filter(Quotes, symbol == c("SIE.DE","CBK.DE"))
#t = subset(Quotes, date == "2007-01-02")
#########


## Option 1: Manual ticker
ticker <- c("GDAXI","SSMI","BIO.DE","ZIL2.DE",
    "SIE.DE","IFX.DE","CBK.DE","2PP.F","BAYN.DE","SDF.DE","KBC.DE")
	# Set name for BRK-A to BRK.A
	setSymbolLookup(GDAXI = list(name = "^GDAXI"))




##Option 2:Load ticker from xlsx

#AllocationCurrent = read.csv("AllocationCurrent.csv", sep="")

#(ticker <- as.vector(AllocationCurrent$Symbol))
ticker <- c("SIE.DE", "CBK.DE", "2PP.F")


setwd(currentPath)
```


```{r plot3}
Quotes_annual_returns <- Quotes %>%
    group_by(symbol) %>%
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "yearly", 
                 type       = "arithmetic")
Quotes_annual_returns



plot3=Quotes_annual_returns %>%
    ggplot(aes(x = date, y = yearly.returns, fill = symbol)) +
    geom_bar(stat = "identity") +
    geom_hline(yintercept = 0, color = palette_light()[[1]]) +
    scale_y_continuous(labels = scales::percent) +
    labs(title = "Quotes: Annual Returns",
         subtitle = "Get annual returns quickly with tq_transmute!",
         y = "Annual Returns", x = "") + 
         facet_wrap(~ symbol, ncol = 2) +
         theme_tq() + 
         scale_fill_tq()
plot3
```

```{r}




Quotes_daily_log_returns <- Quotes %>%
    group_by(symbol) %>%
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "daily", 
                 type       = "log",
                 col_rename = "monthly.returns")

Quotes_daily_log_returns %>%
    ggplot(aes(x = monthly.returns, fill = symbol)) +
    geom_density(alpha = 0.5) +
    labs(title = "Quotes: Charting the Daily Log Returns",
         x = "Monthly Returns", y = "Density") +
         theme_tq() +
         scale_fill_tq() + 
         facet_wrap(~ symbol, ncol = 2)







#Without Periodicity Aggregation

Quotes_daily <- Quotes %>%
    group_by(symbol)

Quotes_daily %>%
    ggplot(aes(x = date, y = adjusted, color = symbol)) +
    geom_line(size = 1) +
    labs(title = "Daily Stock Prices",
         x = "", y = "Adjusted Prices", color = "") +
         facet_wrap(~ symbol, ncol = 2, scales = "free_y") +
         scale_y_continuous(labels = scales::dollar) +
         theme_tq() + 
         scale_color_tq()


#With Periodicity Aggregation

Quotes_monthly <- Quotes %>%
    group_by(symbol) %>%
    tq_transmute(select     = adjusted, 
                 mutate_fun = to.period, 
                 period     = "months")

Quotes_monthly %>%
    ggplot(aes(x = date, y = adjusted, color = symbol)) +
    geom_line(size = 1) +
    labs(title = "Monthly Stock Prices",
         x = "", y = "Adjusted Prices", color = "") +
         facet_wrap(~ symbol, ncol = 2, scales = "free_y") +
         scale_y_continuous(labels = scales::dollar) +
         theme_tq() + 
         scale_color_tq()



# Asset Returns
Quotes_returns_monthly <- Quotes %>%
    group_by(symbol) %>%
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn,
                 period = "monthly",
                 col_rename = "Ra")


# Baseline Returns
baseline_returns_monthly <- "XLK" %>%
    tq_get(get  = "stock.prices",
           from = "2007-01-01", 
           to   = "2017-11-01") %>%
           tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn,
                 period = "monthly",
                 col_rename = "Rb")




#Next, join the asset returns with the baseline returns by date.
############################### make date seq from: getsymbols_irregular data.R
####################
#########################


returns_joined <- left_join(Quotes_returns_monthly, 
                            baseline_returns_monthly,
                            by = "date")
returns_joined

returns_joined <- na.omit(returns_joined)

Quotes_rolling_corr <- returns_joined %>%
    tq_transmute_xy(x          = Ra, 
                    y          = Rb,
                    mutate_fun = runCor,
                    n          = 6,
                    col_rename = "rolling.corr.6")
#And, we can plot the rolling correlations for the Quotes stocks.

Quotes_rolling_corr %>%
    ggplot(aes(x = date, y = rolling.corr.6, color = symbol)) +
    geom_hline(yintercept = 0, color = palette_light()[[1]]) +
    geom_line(size = 1) +
    labs(title = "Quotes: Six Month Rolling Correlation to XLK",
         x = "", y = "Correlation", color = "") +
         facet_wrap(~ symbol, ncol = 2) +
         theme_tq() + 
         scale_color_tq()

Quotes <- na.omit(Quotes)

##Example 4: Use TTR MACD to Visualize Moving Average Convergence Divergence

Quotes_macd <- Quotes %>%
    group_by(symbol) %>%
    tq_mutate(select     = close, 
              mutate_fun = MACD, 
              nFast      = 12, 
              nSlow      = 26, 
              nSig       = 9, 
              maType     = SMA) %>%
              mutate(diff = macd - signal) %>%
              select(-(open:volume))
Quotes_macd
#And, we can visualize the data like so.

Quotes_macd %>%
    filter(date >= as_date("2016-10-01")) %>%
    ggplot(aes(x = date)) + 
    geom_hline(yintercept = 0, color = palette_light()[[1]]) +
    geom_line(aes(y = macd, col = symbol)) +
    geom_line(aes(y = signal), color = "blue", linetype = 2) +
    geom_bar(aes(y = diff), stat = "identity", color = palette_light()[[1]]) +
    facet_wrap(~ symbol, ncol = 2, scale = "free_y") +
    labs(title = "Quotes: Moving Average Convergence Divergence",
         y = "MACD", x = "", color = "") +
         theme_tq() +
         scale_color_tq()



Quotes_macd <- Quotes %>%
    group_by(symbol) %>%
    tq_mutate(select     = close, 
              mutate_fun = RSI, 
              n          = 14, 
              maType     = SMA) 

Quotes_macd

Quotes_macd %>%
    filter(date >= as_date("2016-10-01")) %>%
    ggplot(aes(x = date)) + 
    geom_hline(yintercept = 0, color = palette_light()[[1]]) +
    geom_line(aes(y = SMA, col = symbol))


#Example 5: Use xts apply.quarterly to Get the Max and Min Price for Each Quarter



Quotes
Quotes_max_by_qtr <- Quotes %>%
    group_by(symbol) %>%
    tq_transmute(select = adjusted,
                 mutate_fun = apply.quarterly,
                 FUN = max,
                 col_rename = "max.close") %>%
                 mutate(year.qtr = paste0(year(date), "-Q", quarter(date))) %>%
                 select(-date)
Quotes_max_by_qtr

#The minimum each quarter can be retrieved in much the same way. The data frames can be joined using left_join to get the max and min by quarter.

Quotes_min_by_qtr <- Quotes %>%
    group_by(symbol) %>%
    tq_transmute(select = adjusted,
                 mutate_fun = apply.quarterly,
                 FUN = min,
                 col_rename = "min.close") %>%
                 mutate(year.qtr = paste0(year(date), "-Q", quarter(date))) %>%
                 select(-date)

Quotes_by_qtr <- left_join(Quotes_max_by_qtr, Quotes_min_by_qtr,
                         by = c("symbol" = "symbol",
                                "year.qtr" = "year.qtr"))
Quotes_by_qtr


byQuarterAll <- Quotes_by_qtr %>%
    ggplot(aes(x = year.qtr, color = symbol)) +
    geom_segment(aes(xend = year.qtr, y = min.close, yend = max.close),
                 size = 1) +
                 geom_point(aes(y = max.close), size = 2) +
                 geom_point(aes(y = min.close), size = 2) +
                 facet_wrap(~symbol, ncol = 2, scale = "free_y") +
                 labs(title = "FANG: Min/Max Price By Quarter",
         y = "Stock Price", color = "") +
         theme_tq() +
         scale_color_tq() +
         scale_y_continuous(labels = scales::dollar) +
         theme(axis.text.x = element_text(angle = 90, hjust = 1),
          axis.title.x = element_blank())
byQuarterAll



```

## Portfolio





```{r, eval=FALSE, include=FALSE}
weights <- c(
    0.50, 0.25, 0.25,
     0.50, 0.4, 0.1,
     1, 0, 0
)
stocks <- ticker[1:3]
weights_table <-  tibble(stocks) %>%
    tq_repeat_df(n = n) %>%
    bind_cols(tibble(weights)) %>%
    group_by(portfolio)
weights_table
```


# New weights table

```{r}
#tidyverse
library(readxl)
xlsx_example <- read_excel("AllocationCurrent.xlsx")
xlsx_example



library(openxlsx)
Sys.setenv(R_ZIPCMD = "C:/RBuildTools/3.4/bin/zip")

#wb <- loadWorkbook(file = "OrderBook.xlsx")
#writeData(wb, sheet = 1, x = iris, name = "iris3", startCol = 10)
#Allocation <- read.xlsx("AllocationCurrent.xlsx", namedRegion = "Allocation", detectDates = T)
library(tidyverse)
Allocation <- read.xlsx("AllocationCurrent.xlsx", sheet = 1, startRow = 1, detectDates = T)
Allocation<-Allocation %>%
  group_by(portfolio) %>%
    mutate(weights=Value/sum(Value))


Allocation2 <- read.xlsx("AllocationCurrent.xlsx", sheet = 1, startRow = 1, detectDates = T)


distStocks<-Allocation2 %>%
 distinct(stocks)
distStocks


n = 3
stocks <- distStocks[,1]
weights_table <-  tibble(stocks) %>%
    tq_repeat_df(n = n) %>%
    group_by(portfolio) %>%
    left_join(Allocation) %>%
    replace_na(replace = list(Symbol_short="N/A",weights=0))
    
weights_table<-weights_table %>%
  select(portfolio,stocks,weights)

weights_table




```

#Check missing ticker
```{r}

distStocks<-distStocks%>%
 rename(symbol=stocks)

distStocksAV<-Quotes %>%
 distinct(symbol)
distStocksAV

Ticker<-distStocks %>%
  anti_join(distStocksAV) 
  


```


## Get intraday data from Alpha Vantage

```{r}
Quotes_complete=Quotes
## Source Telegram API
source("R:/7_DataScience/01_R/12_AlphaVantage/alpha_key.R")
## Get data 
for (i in 1:nrow(Ticker)){

S=Ticker[,1][i]
#S="MFST"
QuoteAV<- av_get(symbol = S, av_fun = "TIME_SERIES_DAILY", outputsize = "full")
QuoteAV<- QuoteAV %>%
  mutate(symbol=S)


names(QuoteAV)[1]<-"date"


Quotes_complete<- Quotes_complete %>%
  bind_rows(QuoteAV)
}
  
```


```{r}
Quotes_returns_monthly_complete <- Quotes_complete %>%
    group_by(symbol) %>%
    tq_transmute(select     = close, 
                 mutate_fun = periodReturn,
                 period = "monthly",
                 col_rename = "Ra")
```


#Last day of month
```{r}
library(lubridate)

data=Quotes_returns_monthly_complete
data$date2 <- ymd(data$date)
data$DATE_Month_End <- paste(format(data$date, format="%y-%m"),"-", days_in_month(data$date), sep="")
#OR
last_day <- function(date) {
  ceiling_date(date, "month") - days(1)
}


data2<-data %>%
  mutate(test=last_day(date))%>%
  select(symbol,test,Ra)

test2=spread(data2, symbol, Ra)
```


```{r}
# Single Portfolio depending on n
#https://cran.r-project.org/web/packages/tidyquant/vignettes/TQ05-performance-analysis-with-tidyquant.html

ticker=distStocks

#stock_returns_monthly <- ticker %>%
#    tq_get(get  = "stock.prices",
#           from = "2010-01-01",
#           to   = "2015-12-31") %>%
#           group_by(symbol) %>%
#           tq_transmute(select     = adjusted, 
#                 mutate_fun = periodReturn, 
#                 period     = "monthly", 
#                 col_rename = "Ra")

#replace
stock_returns_monthly=Quotes_returns_monthly_complete



#Second, get baseline asset returns, which is the exact same as Steps 1B and 2B from the Single Portfolio example.
#baseline_returns_monthly <- "XLK" %>%
#baseline_returns_monthly <- "GDAXI" %>%
#    tq_get(get  = "stock.prices",
#           from = "2010-01-01",
 #          to   = "2015-12-31") %>%
  #         tq_transmute(select     = adjusted, 
   #              mutate_fun = periodReturn, 
    #             period     = "monthly", 
      #           col_rename = "Rb")

baseline_returns_monthly



stock_returns_monthly_multi <- stock_returns_monthly %>%
    tq_repeat_df(n = n)
stock_returns_monthly_multi




```

```{r}
#Erros massage when not all assets available
portfolio_returns_monthly_multi <- stock_returns_monthly_multi %>%
    tq_portfolio(assets_col  = symbol, 
                 returns_col = Ra, 
                 weights     = weights_table, 
                 col_rename  = "Ra")
portfolio_returns_monthly_multi



RaRb_multiple_portfolio <- left_join(portfolio_returns_monthly_multi, 
                                     baseline_returns_monthly,
                                     by = "date")
RaRb_multiple_portfolio




RaRb_multiple_portfolio <- na.omit(RaRb_multiple_portfolio)



```

```{r}
library(tidyquant)
P_CAPM=RaRb_multiple_portfolio %>%
    tq_performance(Ra = Ra, Rb = Rb, performance_fun = table.CAPM)
P_CAPM
```




```{r}
P_SR=RaRb_multiple_portfolio %>%
    tq_performance(Ra = Ra, Rb = NULL, performance_fun = SharpeRatio)

P_VaR <- RaRb_multiple_portfolio %>%
    tq_performance(Ra = Ra, Rb = NULL, performance_fun = VaR, portfolio_method="component")
P_VaR


#tq_performance_fun_options()

P_Stats<-RaRb_multiple_portfolio %>%
    tq_performance(Ra = Ra, Rb = NULL, performance_fun = table.Stats)

data(managers)
chart.VaRSensitivity(managers[,1,drop=FALSE],
		methods=c("HistoricalVaR", "ModifiedVaR", "GaussianVaR"),
		colorset=bluefocus, lwd=2)

```


VaR(R, p = 0.95, method = c("modified", "gaussian","historical", "kernel"),
           clean = c("none", "boudt", "geltner"),
                 portfolio_method = c("single", "component","marginal"),
                 weights = NULL, mu = NULL, sigma = NULL,
                 m3 = NULL, m4 = NULL, invert = TRUE, ...)


## Customizing tq_performance

```{r}
library(knitr)
library(kableExtra)

args(SharpeRatio)
RaRb_multiple_portfolio %>%
    tq_performance(Ra              = Ra, 
                   performance_fun = SharpeRatio)

tbl=RaRb_multiple_portfolio %>%
    tq_performance(Ra              = Ra, 
                   performance_fun = SharpeRatio,
                   Rf              = 0.03 / 12)

kable(tbl)
kable(tbl, format = "latex", booktabs = T)
dt <- mtcars[1:5, 1:6]

dt %>%
  kable("html") %>%
  kable_styling()
kable(dt, format = "latex", booktabs = T)
```




# CHARTS

```{r}




args(Return.portfolio)

wts_map <- tibble(
    symbols = c(ticker[1:2]),
    weights = c(0.5, 0.5)
)
wts_map




portfolio_returns_monthly <- stock_returns_monthly %>%
    tq_portfolio(assets_col = symbol,
                 returns_col = Ra,
                 weights = wts_map,
                 col_rename = "Ra")



portfolio_returns_monthly %>%
    ggplot(aes(x = date, y = Ra)) +
    geom_bar(stat = "identity", fill = palette_light()[[1]]) +
    labs(title = "Portfolio Returns",
         subtitle = "50% AAPL, 0% GOOG, and 50% NFLX",
         caption = "Shows an above-zero trend meaning positive returns",
         x = "", y = "Monthly Returns") +
         geom_smooth(method = "lm") +
         theme_tq() +
         scale_color_tq() +
         scale_y_continuous(labels = scales::percent)


#Custom

portfolio_growth_monthly <- stock_returns_monthly %>%
    tq_portfolio(assets_col = symbol,
                 returns_col = Ra,
                 weights = wts_map,
                 col_rename = "investment.growth",
                 wealth.index = TRUE) %>%
                 mutate(investment.growth = investment.growth * 10000)


portfolio_growth_monthly %>%
    ggplot(aes(x = date, y = investment.growth)) +
    geom_line(size = 2, color = palette_light()[[1]]) +
    labs(title = "Portfolio Growth",
         subtitle = "50% AAPL, 0% GOOG, and 50% NFLX",
         caption = "Now we can really visualize performance!",
         x = "", y = "Portfolio Value") +
         geom_smooth(method = "loess") +
         theme_tq() +
         scale_color_tq() +
         scale_y_continuous(labels = scales::dollar)












```


#CHARTS

# Multiple Portfolios

```{r}


portfolio_growth_monthly_multi <- stock_returns_monthly_multi %>%
    tq_portfolio(assets_col = symbol,
                 returns_col = Ra,
                 weights = weights_table,
                 col_rename = "investment.growth",
                 wealth.index = TRUE) %>%
                 mutate(investment.growth = investment.growth * 10000)


portfolio_growth_monthly_multi %>%
    ggplot(aes(x = date, y = investment.growth, color = factor(portfolio))) +
    geom_line(size = 2) +
    labs(title = "Portfolio Growth",
         subtitle = "Comparing Multiple Portfolios",
         caption = "Portfolio 3 is a Standout!",
         x = "", y = "Portfolio Value",
         color = "Portfolio") +
         geom_smooth(method = "loess") +
         theme_tq() +
         scale_color_tq() +
         scale_y_continuous(labels = scales::dollar)
```


```{r}
tq_performance_fun_options()
```






